Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-28 pnas/Towards.tex
small modifications

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec_incl_noisy.eps}
		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
	\end{subfigure} 
	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
		\revised{The reconstructions from autocorrelations estimated from noisy data are shown in gray, the reconstructions from clean autocorrelations in yellow, the (smoothed) ground truths in blue, and the original molecules are shown in purple} to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion. \revised{For the noisy experiment, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI - we present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}}
%		 \vspace{-20pt} 	
\end{figure}
% -------------- Vertical subfigures: -------------------------------

>>>>

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec_incl_noisy.eps}
		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
	\end{subfigure} 
	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
		\revised{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
		The reconstructions  from clean autocorrelations are shown in yellow and recovery from 
		autocorrelations estimated from noisy data in gray. For the noisy experiments, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI. We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}.}
		 \vspace{-20pt} 	
\end{figure}
% -------------- Vertical subfigures: -------------------------------
